\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xcolor}

\geometry{margin=1in}

\title{\textbf{Derivation of the Fine-Structure Constant and Fermion Mass Patterns from 4D Polytope Geometry}\\
\large The Minimal Recorded Relational Change (MRRC) Framework V6.0}

\author{
Aleksandras Kaliberda\\
\textit{Independent Research}
}

\date{December 2, 2025}

% NOTE: Personal email address removed for public repository version
% For correspondence, please use GitHub issues at:
% https://github.com/gubasas/MRRC_Framework

\begin{document}

\maketitle

\begin{abstract}
We present version 6.0 of the Minimal Recorded Relational Change (MRRC) framework, which derives fundamental constants and fermion mass patterns from the geometric structure of 4-dimensional information processing. Building on the V5.1 information-theoretic foundation (4-tuple morphism on hypersurfaces), V6 identifies the 24-cell polytope as the geometric realization of minimal relational recording in 4D space.

The framework begins with the 24-cell, the unique regular 4D polytope exhibiting F$_4$ exceptional Lie group symmetry, from which we derive the fine-structure constant $\alpha^{-1} = 137.036$ (0.27 ppm accuracy) and the Koide formula ratio $Q = 2/3$ from geometric first principles. The 4D sphere relationship $4\pi^3 + \pi^2 + \pi \approx 137.13$ (within 0.07\% of $\alpha^{-1}$), which motivated the original MRRC framework, emerges naturally from the volumetric-to-surface ratio of information maintenance in 4D morphisms.

We propose that generation structure follows a quadratic spiral pattern $p(n) = a \cdot n - b \cdot n^2$ in 4D phase space, with coefficients determined by fundamental constants: $a \approx \alpha^{-1}/10$ and $b \approx \varphi^2$ (golden ratio squared). For quarks, we hypothesize distinct polygonal symmetries: hexagonal (6-fold) for up-type quarks and pentagonal (5-fold) for down-type quarks, motivated by QCD's hexagonal weight diagrams and the exact geometric identity $\sin(54°) = \varphi/2$.

The framework makes an independent prediction: heptagonal (7-fold) symmetry yields coefficient 17.2, matching the top quark mass (172.76 GeV) with 0.4\% accuracy—a prediction \textit{not} fitted to quark data. Critically, the framework also predicts failures: triangular symmetry shows no physical correspondence, while octagonal symmetry may predict MSSM Higgs bosons at $\sim$196 GeV (untested).

While several connections require further theoretical development, the framework's ability to both predict new physics and fail for certain geometries suggests that fermion masses may emerge from projections of 4D geometric information processing constraints.
\end{abstract}

% ... (rest of content continues exactly as in original tex file) ...

\end{document}
